MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-28 paper.Rmd
Better conclusion.

The new `R` packages enable the creation of databases of primary, final, and useful stage
energy and exergy energy conversion chains.
Such databases will enable advances in societal exergy analysis community
and lead to greater insights on economic growth and human well-being.

@@

Do we have any acknowledgements?

>>>>

The new `R` packages described in this paper
enable the creation of databases of primary, final, and useful
energy and exergy conversion chains.
Such databases will enable advances in the societal exergy analysis community
and lead to greater insights 
about the role of energy 
in economic growth and human well-being.

@@
